\begin{center}
\begin{longtable}{|p{0.15\textwidth}|p{0.25\textwidth}|p{0.5\textwidth}|}
\caption{Prediction examples produced by \ours for CommonsenseQA.}
\label{tab:example_commonsenseqa}\\

\toprule \multicolumn{1}{|c|}{\textbf{Category}} & \multicolumn{1}{c|}{\textbf{Question}} & \multicolumn{1}{c|}{\textbf{Answer}} \\ \midrule 
\endfirsthead

\multicolumn{3}{c}%
{{\tablename\ \thetable{} -- Continued from previous page}} \\
\toprule \multicolumn{1}{|c|}{\textbf{Category}} & \multicolumn{1}{c|}{\textbf{Question}} & \multicolumn{1}{c|}{\textbf{Answer}} \\ \midrule
\endhead

\multicolumn{3}{|r|}{{Continued on next page}} \\ \bottomrule
\endfoot

\bottomrule
\endlastfoot

Correct - CoT is correct &Q: If there is a pond with trees around it, where it it likely located? Answer Choices: (A) ground (B) bathroom (C) forest (D) countryside (E) rural area &A: Let's think step by step. A pond is likely to be located near trees because trees need water to survive. Therefore, the most likely location for a pond with trees around it is in a forest. Therefore, among A through E, the answer is C. \okmark \\

\midrule

Correct - CoT is correct &Q: Human beings learn about current events from what print item? Answer Choices: (A) question authority (B) melt (C) read newspapers (D) act (E) dictionary &A: Let's think step by step. How do human beings learn? They learn by observing and listening to others, and they also learn by reading. So it's most likely that human beings learn about current events from reading newspapers. Therefore, among A through E, the answer is C. \okmark \\

\midrule

%Correct - CoT is correct &Q: Where can you find a dogs house? Answer Choices: (A) found outside (B) faithful (C) frightening (D) cold (E) four legs &A: Let's think step by step. A dog needs a house to protect it from the weather and predators. The house should be big enough for the dog to move around in, but not too big or the dog will be cold. The house should have a door to keep out the cold and a roof to keep out the rain. The house should be made of sturdy materials that will not collapse in the wind. The best place to find a dog house is at a pet store or a home improvement store. You can also find dog houses online. Therefore, among A through E, the answer is A. \\
%\midrule

Correct - CoT is correct &Q: The artist was sitting quietly pondering, then suddenly he began to paint when what struck him? Answer Choices: (A) sadness (B) anxiety (C) inspiration (D) discomfort (E) insights &A: Let's think step by step. The first thing that happens is that the artist is sitting quietly and pondering. This means he's thinking deeply about something, probably trying to come up with an idea. Then, suddenly, he begins to paint. This means he was inspired by something he thought of. The most likely explanation is that he had an insight, or a sudden realization, that led him to start painting. Therefore, among A through E, the answer is most likely (C), inspiration. \okmark \\

\midrule

Correct - CoT is \par \textbf{INCORRECT} &Q: What is likely to satisfy someone's curiosity? Answer Choices: (A) hear news (B) read book (C) see favorite show (D) comedy show (E) go somewhere &A: Let's think step by step. In order to satisfy someone's curiosity, they would need to want to know more about something. So, (A) hearing news and (B) reading a book are both good answers because they provide information that the person may be curious about. (C) Seeing a favorite show could also work because it might be something the person is curious about and wants to know more about. (D) A comedy show could potentially satisfy someone's curiosity if the person is curious about the comedian's life or what they are like in person. (E) Going somewhere could also work if the person is curious about a certain place and wants to know more Therefore, among A through E, the answer is A, B, C, D, or E. \okmark \bred{(Model cannot choose only one.)} \bblue{(GT : (A), \theirsz : (E))} \\

\midrule

Correct - CoT is \par \textbf{INCORRECT} &Q: What would be necessary for getting in shape? Answer Choices: (A) good health (B) exercise (C) muscle tone (D) sweat (E) feel better &A: Let's think step by step. In order to get in shape, you need to be able to do three things: 1. Exercise regularly 2. Eat a healthy diet 3. Get enough sleep If you can do all three of those things, then you will be well on your way to getting in shape! Therefore, among A through E, the answer is B, C, and D. \okmark \bred{(Model cannot choose only one.)} \bblue{(GT : (B), \theirsz : (B))}\\

\midrule

Correct - CoT is \par \textbf{INCORRECT} &Q: The man had a fear of illness, so he never visited friends who were a what? Answer Choices: (A) sick person (B) hospital (C) elderly person (D) graveyard (E) doctor's office &A: Let's think step by step. The man has a fear of illness, so he would avoid anything that would put him in close proximity to an ill person. This would include a hospital, where sick people are treated, and a doctor's office, where sick people go to receive care. An elderly person is more likely to be ill than a young person, so the man would avoid them as well. A graveyard is where people who have died from illness are buried, so the man would avoid that as well. The answer is A, sick person. Therefore, among A through E, the answer is A. \okmark \bred{(Model cannot narrow down choice to one in CoT.)} \bblue{(GT : (A), \theirsz : (A))}\\

\midrule

CommonSense Mistake &Q: Where is a well used toy car likely to be found? Answer Choices: (A) child's room (B) boy's bedroom (C) own home (D) toy store (E) house &A: Let's think step by step. A toy car is likely to be found in a child's room. A child's room is likely to be found in a house. Therefore, a toy car is likely to be found in a house. Therefore, among A through E, the answer is E. \ngmark \myspace \bblue{(GT : (A), \theirsz : (A))}\\

\midrule

CommonSense Mistake &Q: Where can you go to use a piano in your neighborhood if you don't have one? Answer Choices: (A) music school (B) music store (C) neighbor's house (D) lunch (E) drawing room &A: Let's think step by step. If you don't have a piano, you can't use your own. You could go to a music school, but that seems like it would be for a lesson rather than just to use a piano. A music store might have a piano that you could use, but you would probably have to buy something. You could go to a neighbor's house, but that seems like a lot to ask. You could go to a lunch, but that doesn't make sense. You could go to a drawing room, but that also doesn't make sense. The answer must be (B) music store. Therefore, among A through E, the answer is B. \ngmark \myspace \bblue{(GT : (C), \theirsz : (C))}\\

\midrule

CommonSense Mistake &Q: David watched some nesting birds using his binoculars while on vacation. Where might David be?. Answer Choices: (A) sky (B) vaccation (C) forest (D) countryside (E) roof &A: Let's think step by step. First, we need to understand what the word "binoculars" means. Binoculars are two telescopes that are joined together and allow a person to see things that are far away. Now, we need to think about where a person might use binoculars. A person might use binoculars to see things that are far away and in the sky, or to see things that are far away and on the ground. So, the answer could be either (A) sky or (D) countryside. Therefore, among A through E, the answer is (A) or (D). \ngmark \myspace \bblue{(GT : (C), \theirsz : (D))} \\

\midrule

CommonSense Mistake &Q: When you get up in the morning before you begin work you should do what? Answer Choices: (A) apply for job (B) sleep (C) concentrate (D) shower (E) just do &A: Let's think step by step. The first thing you should do when you wake up is probably to stretch and yawn to get your body moving. Then, you should probably brush your teeth and wash your face to get ready for the day. After that, you might want to eat breakfast to give yourself some energy for the day. Once you're all set, you can start your work for the day. Therefore, among A through E, the answer is C.  \ngmark \myspace \bblue{(GT : (D), \theirsz : (C))} \\

\midrule

CommonSense Mistake &Q: What is someone doing if he or she is sitting quietly and his or her eyes are moving? Answer Choices: (A) reading (B) meditate (C) fall asleep (D) bunk (E) think &A: Let's think step by step. If someone is sitting quietly, that means they are not moving around. And if their eyes are moving, they are probably not asleep. So it's probably not (C) or (D). If they are reading, they would be looking at the book, not moving their eyes around, so it's probably not (A), which leaves us with (B) and (E). It's more likely that they are thinking, so (E) is the best answer. Therefore, among A through E, the answer is E. \ngmark \myspace \bblue{(GT : (A), \theirsz : (E))}\\

\midrule

%Factual Mistake &Q: What are candles good for eliminating? Answer Choices: (A) shelf (B) board (C) church (D) table (E) dark &A: Let's think step by step. Candles are often used for light, so (E) dark is probably not the answer. Candles are also used for decoration or to make a place smell nice, so (A) shelf, (B) board, (C) church, and (D) table are all possible answers. Therefore, among A through E, the answer is probably (A), (B), (C), or (D). \\

%\midrule

Logical \par Mistake &Q: If you really wanted a grape, where would you go to get it? Answer Choices: (A) winery (B) fruit stand (C) field (D) kitchen (E) food &A: Let's think step by step. If you want a grape, the first place you might think to look is a fruit stand. If there are no grapes at the fruit stand, your next best bet would be a grocery store. If there are no grapes at the grocery store, you might try a vineyard or winery. If there are no grapes at the vineyard or winery, your last resort would be to grow your own grapes. Therefore, among A through E, the answer is E. \ngmark \myspace \bblue{(GT : (B), \theirsz : (B))}\\

%\bottomrule

\end{longtable}
\end{center}