% This must be in the first 5 lines to tell arXiv to use pdfLaTeX, which is strongly recommended.
\pdfoutput=1
% In particular, the hyperref package requires pdfLaTeX in order to break URLs across lines.

\documentclass[11pt]{article}

% Remove the "review" option to generate the final version.
\usepackage{EMNLP2022}
\usepackage{lipsum}
% Standard package includes
\usepackage{times}
\usepackage{latexsym}

\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{booktabs} % for professional tables
\usepackage{lipsum}
\usepackage{amsmath}
\usepackage{amssymb, amsthm, latexsym}
\usepackage{multirow}

\usepackage{nicefrac}

% \usepackage{minted}
\usepackage[frozencache,cachedir=.]{minted}
\newminted{python}{%
    % options to customize output of pythoncode
}


% For proper rendering and hyphenation of words containing Latin characters (including in bib files)
\usepackage[T1]{fontenc}
% For Vietnamese characters
% \usepackage[T5]{fontenc}
% See https://www.latex-project.org/help/documentation/encguide.pdf for other character sets

% This assumes your files are encoded as UTF8
\usepackage[utf8]{inputenc}

% This is not strictly necessary, and may be commented out.
% However, it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

% This is also not strictly necessary, and may be commented out.
% However, it will improve the aesthetics of text in
% the typewriter font.
\usepackage{inconsolata}

% If the title and author information does not fit in the area allocated, uncomment the following
%
%\setlength\titlebox{<dim>}
%
% and set <dim> to something 5cm or larger.

\title{\textsc{Petals}: Collaborative Inference and Fine-tuning of Large Models}

% Author information can be set in various styles:
% For several authors from the same institution:
% \author{Author 1 \and ... \and Author n \\
%         Address line \\ ... \\ Address line}
% if the names do not fit well on one line use
%         Author 1 \\ {\bf Author 2} \\ ... \\ {\bf Author n} \\
% For authors from different institutions:
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \And  ... \And
%         Author n \\ Address line \\ ... \\ Address line}
% To start a seperate ``row'' of authors use \AND, as in
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \AND
%         Author 2 \\ Address line \\ ... \\ Address line \And
%         Author 3 \\ Address line \\ ... \\ Address line}

\author{Alexander Borzunov\thanks{~~Equal contribution.\newline Correspondence to: \texttt{petals-dev@googlegroups.com}}\\
  Yandex \\\And
  Dmitry Baranchuk$^*$ \\
  Yandex \\\And
  Tim Dettmers$^*$ \\
  University of Washington\\\AND
  Max Ryabinin$^*$ \\
  Yandex \\\And
  Younes Belkada$^*$ \\
  Hugging Face, ENS Paris-Saclay \\\And
  Artem Chumachenko \\
  Yandex \\\AND
  Pavel Samygin \\
  Yandex School of Data Analysis \\\And
  Colin Raffel \\
  Hugging Face
  }

\begin{document}
\maketitle
\begin{abstract}

Many NLP tasks
benefit from using large language models (LLMs) that often have more than 100 billion parameters. With the release of BLOOM-176B and OPT-175B, everyone can download pretrained models of this scale.
Still, using these models requires high-end hardware unavailable to many researchers. 
In some cases, LLMs can be used more affordably via RAM offloading or hosted APIs. However, these techniques have innate limitations: offloading is too slow for interactive inference, while APIs are not flexible enough for research.
In this work, we propose \textsc{Petals}\footnote{~~\textsc{Petals} source code and documentation are available at \texttt{\href{https://petals.ml}{https://petals.ml}}} --- a~system for inference and fine-tuning of large models collaboratively by joining the resources of multiple parties trusted to process client's data.
We demonstrate that this strategy significantly outperforms offloading for very large models, running inference of BLOOM-176B on consumer GPUs with $\approx$ 1 step per second.
Unlike most inference APIs, \textsc{Petals} also natively exposes the hidden states of served models, allowing its users to train and share custom model extensions based on efficient fine-tuning methods.


\end{abstract}

\input{intro}

\input{design}

\input{internals}

\input{discussion}

\section*{Acknowledgements}
The authors would like to thank Zheng-Xin Yong, Ilya Dimov, Yozh, Teven Le Scao, Stas Bekman, and Haokun Liu for helpful discussions. We also thank Teven Le Scao for his help in designing Figure~\ref{fig:overview}. A part of the experiments was conducted on a personal server of Elena Voita.

% Entries for the entire Anthology, followed by custom entries
\bibliography{anthology,custom}
\bibliographystyle{acl_natbib}

% \appendix

% \section{Example Appendix}
% \label{sec:appendix}

% This is an appendix.

\end{document}
